\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-06-08 manuscript/main.tex
modified:   analysis/final_analysis.do 	modified:   figures/did_1.pdf 	modified:   figures/did_2.pdf 	modified:   figures/did_3.pdf 	deleted:    manuscript/main.aux 	deleted:    manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	deleted:    manuscript/main.fls 	deleted:    manuscript/main.log 	deleted:    manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   result_tables/difference_in_difference.tex 	modified:   result_tables/dynamic.tex 	modified:   result_tables/entry_effect.tex 	new file:   resu

\title{ \vspace*{-2.5cm} \hspace*{-0.5cm}Evaluating the Impact of Offline Store Clusters in the Age of Platforms: Evidence from China's Metropolitan Real Estate Market \footnote{
The preliminary version was entitled "Property brokerage, Partial monopoly and Housing market" and was presented at The 1st Summer Meeting in Urban Economics, China. We are grateful for the comments and suggestions made at the meeting. The code to replicate the paper can be accessed at \href{https://github.com/sergiozxy/RealEstateBrokerage}{https://github.com/sergiozxy/RealEstateBrokerage} The authors gratefully acknowledge financial support from the Fundamental Research Funds for the Central Universities of Sichuan University (2019hhf-08; SKSYL201812; 2018jj-01) and National Natural Science Foundation of China (71773081). % We gratefully thank for Hanying Liu from Sichuan University and Chongyu Wang from Florida State University for insightful feedback.
}}

@@

\textbf{Now I think about how to do this, the first task is to write completely the model and estimation of the offline and platform's effect with offline is the brokerage's offline store's entry and the onlien is the platofmrization strategy.}

@@

>>>>

\title{ \vspace*{-2.5cm} \hspace*{-0.5cm}Evaluating the Impact of Offline Store Clusters under the Consolidation: Evidence from China's Metropolitan Real Estate Market \footnote{
The preliminary version was entitled "Property brokerage, Partial monopoly and Housing market" and was presented at The 1st Summer Meeting in Urban Economics, China. We are grateful for the comments and suggestions made at the meeting. The code to replicate the paper can be accessed at \href{https://github.com/sergiozxy/RealEstateBrokerage}{https://github.com/sergiozxy/RealEstateBrokerage} The authors gratefully acknowledge financial support from the Fundamental Research Funds for the Central Universities of Sichuan University (2019hhf-08; SKSYL201812; 2018jj-01) and National Natural Science Foundation of China (71773081). % We gratefully thank for Hanying Liu from Sichuan University and Chongyu Wang from Florida State University for insightful feedback.
}}

@@

@@

% Brokerage consolidation refers to the process by which a larger real estate brokerage firm integrates multiple smaller brokerage firms into a single, unified platform.
